### 2020-10-14 submission/manuscript.Rmd
Edits from proofs

Antibiotics are a common risk factor for *Clostridioides difficile* infections (CDIs) due to their effect on the intestinal microbiota, but there is variation in who goes on to develop severe or recurrent CDIs after exposure [@Teng2019; @Kelly2012]. Additionally, asymptomatic colonization, where *C. difficile* is detectable, but symptoms are absent, has been documented in infants and adults [@Zacharioudakis2015; @Crobach2018]. The intestinal microbiota has been implicated in asymptomatic colonization [@Zhang2015; @VanInsberghe2020], susceptibility to CDIs [@Mancabelli2017, @Duvallet2017], and adverse CDI outcomes [@Seekatz2016; @Khanna2016; @Pakpour2017; @Lee2020]. However, it is not clear how much inter-individual microbiota variation contributes to the range of outcomes observed after *C. difficile* exposure relative to other risk factors.

@@

Other microbiota and host factors that were outside the scope of our current study may also contribute to the differences in *C. difficile* colonization dynamics between sources of mice. The microbiota is composed of viruses, fungi, and parasites in addition to bacteria, and these non-bacterial members can also vary across sources of mice [@Rasmussen2019; @Mims2020]. While our study focused solely on the bacterial portion, viruses and fungi have also begun to be implicated in the context of CDIs or FMT treatments for recurrent CDIs [@Markey2018; @Stewart2019; @Ott2017; @Zuo2017; @Zuo2018]. Beyond community composition, the metabolic function of the microbiota also has a CDI signature [@Robinson2019; @Jenior2017; @Fletcher2018; @Jump2014] and can vary across mice from different sources [@Xiao2015]. For example, microbial metabolites, particularly secondary bile acids and butyrate production, have been implicated as important contributors to *C. difficile* resistance [@Buffie2014; @Lawley2012]. Interestingly, butyrate has previously been shown to vary across mouse vendors and mediated resistance to *Citrobacter rodentium* infection, a model of enterohemorrhagic and enteropathogenic *Escherichia coli* infections [@Osbelt2020]. Evidence for immunological toning differences in IgA and Th17 cells across mice from different vendors have also been documented [@Fransen2015; @Ivanov2009] and could influence the host response to CDI [@Azrad2018; @Saleh2019], particularly relevant for *C. difficile* strains that induce more severe disease than *C. difficile* 630. The outcome after *C. difficile* exposure depends on a multitude of factors, including genetics, age, diet, and immunity; all of which also influence the microbiota.

@@

**(i) Animals.** All experiments were approved by the University of Michigan Animal Care and Use Committee (IACUC) under protocol number PRO00006983. Female C57BL/7 mice were obtained from 6 different sources: The Jackson Laboratory, Charles River Laboratories, Taconic Biosciences, Envigo, and two colonies at the University of Michigan (the Schloss lab colony and the Young lab colony). The Young lab colony was originally established with mice purchased from Jackson in 2002, and the Schloss lab colony was established in 2010 with mice donated from the Young lab. The 4 groups of mice purchased from vendors were allowed to acclimate to the University of Michigan mouse facility for 13 days prior to starting the experiment. At least 4 female mice (age 5-10 weeks) were obtained per source and mice from the same source were primarily housed at a density of 2 mice per cage. The experiment was repeated once, approximately 3 months after the start of the first experiment.

>>>>

Antibiotics are a common risk factor for *Clostridioides difficile* infections (CDIs) due to their effect on the intestinal microbiota, but there is variation in who goes on to develop severe or recurrent CDIs after exposure [@Teng2019; @Kelly2012]. Additionally, asymptomatic colonization, where *C. difficile* is detectable, but symptoms are absent, has been documented in infants and adults [@Zacharioudakis2015; @Crobach2018]. The intestinal microbiota has been implicated in asymptomatic colonization [@Zhang2015; @VanInsberghe2020], susceptibility to CDIs [@Mancabelli2017; @Duvallet2017], and adverse CDI outcomes [@Seekatz2016; @Khanna2016; @Pakpour2017; @Lee2020]. However, it is not clear how much inter-individual microbiota variation contributes to the range of outcomes observed after *C. difficile* exposure relative to other risk factors.

@@

Other microbiota and host factors that were outside the scope of our current study may also contribute to the differences in *C. difficile* colonization dynamics between sources of mice. The microbiota is composed of viruses, fungi, and parasites in addition to bacteria, and these non-bacterial members can also vary across sources of mice [@Rasmussen2019; @Mims2020]. While our study focused solely on the bacterial portion, viruses and fungi have also begun to be implicated in the context of CDIs or fecal microbiota transplant (FMT) treatments for recurrent CDIs [@Markey2018; @Stewart2019; @Ott2017; @Zuo2017; @Zuo2018]. Beyond community composition, the metabolic function of the microbiota also has a CDI signature [@Robinson2019; @Jenior2017; @Fletcher2018; @Jump2014] and can vary across mice from different sources [@Xiao2015]. For example, microbial metabolites, particularly secondary bile acids and butyrate production, have been implicated as important contributors to *C. difficile* resistance [@Buffie2014; @Lawley2012]. Interestingly, butyrate has previously been shown to vary across mouse vendors and mediated resistance to *Citrobacter rodentium* infection, a model of enterohemorrhagic and enteropathogenic *Escherichia coli* infections [@Osbelt2020]. Evidence for immunological toning differences in IgA and Th17 cells across mice from different vendors have also been documented [@Fransen2015; @Ivanov2009] and could influence the host response to CDI [@Azrad2018; @Saleh2019], particularly relevant for *C. difficile* strains that induce more severe disease than *C. difficile* 630. The outcome after *C. difficile* exposure depends on a multitude of factors, including genetics, age, diet, and immunity; all of which also influence the microbiota.

@@

**(i) Animals.** All experiments were approved by the University of Michigan Animal Care and Use Committee (IACUC) under protocol number PRO00006983. Female C57BL/6 mice were obtained from 6 different sources: The Jackson Laboratory, Charles River Laboratories, Taconic Biosciences, Envigo, and two colonies at the University of Michigan (the Schloss lab colony and the Young lab colony). The Young lab colony was originally established with mice purchased from Jackson in 2002, and the Schloss lab colony was established in 2010 with mice donated from the Young lab. The 4 groups of mice purchased from vendors were allowed to acclimate to the University of Michigan mouse facility for 13 days prior to starting the experiment. At least 4 female mice (age 5-10 weeks) were obtained per source and mice from the same source were primarily housed at a density of 2 mice per cage. The experiment was repeated once, approximately 3 months after the start of the first experiment.

### 2020-10-14 submission/manuscript.tex
Edits from proofs

Antibiotics are a common risk factor for \emph{Clostridioides difficile}
infections (CDIs) due to their effect on the intestinal microbiota, but
there is variation in who goes on to develop severe or recurrent CDIs
after exposure (1, 2). Additionally, asymptomatic colonization, where
\emph{C. difficile} is detectable, but symptoms are absent, has been
documented in infants and adults (3, 4). The intestinal microbiota has
been implicated in asymptomatic colonization (5, 6), susceptibility to
CDIs (7), and adverse CDI outcomes (9--12). However, it is not clear how
much inter-individual microbiota variation contributes to the range of
outcomes observed after \emph{C. difficile} exposure relative to other
risk factors.

@@

Other microbiota and host factors that were outside the scope of our
current study may also contribute to the differences in \emph{C.
difficile} colonization dynamics between sources of mice. The microbiota
is composed of viruses, fungi, and parasites in addition to bacteria,
and these non-bacterial members can also vary across sources of mice
(56, 57). While our study focused solely on the bacterial portion,
viruses and fungi have also begun to be implicated in the context of
CDIs or FMT treatments for recurrent CDIs (35, 58--61). Beyond community
composition, the metabolic function of the microbiota also has a CDI
signature (20, 47, 62, 63) and can vary across mice from different
sources (64). For example, microbial metabolites, particularly secondary
bile acids and butyrate production, have been implicated as important
contributors to \emph{C. difficile} resistance (33, 44). Interestingly,
butyrate has previously been shown to vary across mouse vendors and
mediated resistance to \emph{Citrobacter rodentium} infection, a model
of enterohemorrhagic and enteropathogenic \emph{Escherichia coli}
infections (23). Evidence for immunological toning differences in IgA
and Th17 cells across mice from different vendors have also been
documented (65, 66) and could influence the host response to CDI (67,
68), particularly relevant for \emph{C. difficile} strains that induce
more severe disease than \emph{C. difficile} 630. The outcome after
\emph{C. difficile} exposure depends on a multitude of factors,
including genetics, age, diet, and immunity; all of which also influence
the microbiota.

@@

\textbf{(i) Animals.} All experiments were approved by the University of
Michigan Animal Care and Use Committee (IACUC) under protocol number
PRO00006983. Female C57BL/7 mice were obtained from 6 different sources:
The Jackson Laboratory, Charles River Laboratories, Taconic Biosciences,
Envigo, and two colonies at the University of Michigan (the Schloss lab
colony and the Young lab colony). The Young lab colony was originally
established with mice purchased from Jackson in 2002, and the Schloss
lab colony was established in 2010 with mice donated from the Young lab.
The 4 groups of mice purchased from vendors were allowed to acclimate to
the University of Michigan mouse facility for 13 days prior to starting
the experiment. At least 4 female mice (age 5-10 weeks) were obtained
per source and mice from the same source were primarily housed at a
density of 2 mice per cage. The experiment was repeated once,
approximately 3 months after the start of the first experiment.

>>>>

Antibiotics are a common risk factor for \emph{Clostridioides difficile}
infections (CDIs) due to their effect on the intestinal microbiota, but
there is variation in who goes on to develop severe or recurrent CDIs
after exposure (1, 2). Additionally, asymptomatic colonization, where
\emph{C. difficile} is detectable, but symptoms are absent, has been
documented in infants and adults (3, 4). The intestinal microbiota has
been implicated in asymptomatic colonization (5, 6), susceptibility to
CDIs (7, 8), and adverse CDI outcomes (9--12). However, it is not clear
how much inter-individual microbiota variation contributes to the range
of outcomes observed after \emph{C. difficile} exposure relative to
other risk factors.

@@

Other microbiota and host factors that were outside the scope of our
current study may also contribute to the differences in \emph{C.
difficile} colonization dynamics between sources of mice. The microbiota
is composed of viruses, fungi, and parasites in addition to bacteria,
and these non-bacterial members can also vary across sources of mice
(56, 57). While our study focused solely on the bacterial portion,
viruses and fungi have also begun to be implicated in the context of
CDIs or fecal microbiota transplant (FMT) treatments for recurrent CDIs
(35, 58--61). Beyond community composition, the metabolic function of
the microbiota also has a CDI signature (20, 47, 62, 63) and can vary
across mice from different sources (64). For example, microbial
metabolites, particularly secondary bile acids and butyrate production,
have been implicated as important contributors to \emph{C. difficile}
resistance (33, 44). Interestingly, butyrate has previously been shown
to vary across mouse vendors and mediated resistance to
\emph{Citrobacter rodentium} infection, a model of enterohemorrhagic and
enteropathogenic \emph{Escherichia coli} infections (23). Evidence for
immunological toning differences in IgA and Th17 cells across mice from
different vendors have also been documented (65, 66) and could influence
the host response to CDI (67, 68), particularly relevant for \emph{C.
difficile} strains that induce more severe disease than \emph{C.
difficile} 630. The outcome after \emph{C. difficile} exposure depends
on a multitude of factors, including genetics, age, diet, and immunity;
all of which also influence the microbiota.

@@

\textbf{(i) Animals.} All experiments were approved by the University of
Michigan Animal Care and Use Committee (IACUC) under protocol number
PRO00006983. Female C57BL/6 mice were obtained from 6 different sources:
The Jackson Laboratory, Charles River Laboratories, Taconic Biosciences,
Envigo, and two colonies at the University of Michigan (the Schloss lab
colony and the Young lab colony). The Young lab colony was originally
established with mice purchased from Jackson in 2002, and the Schloss
lab colony was established in 2010 with mice donated from the Young lab.
The 4 groups of mice purchased from vendors were allowed to acclimate to
the University of Michigan mouse facility for 13 days prior to starting
the experiment. At least 4 female mice (age 5-10 weeks) were obtained
per source and mice from the same source were primarily housed at a
density of 2 mice per cage. The experiment was repeated once,
approximately 3 months after the start of the first experiment.
